\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\title{Problem Statement and Goals\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
Date1 & Name(s) & Description of changes\\
\bottomrule
\end{tabularx}
\end{table}

\section{Problem Statement}

\subsection{Problem}
Microrobots are being explored in minimally invasive surgeries due to their ability to navigate millimeter spaces. The magnetic actuation systems used to control these microrobots suffer from bulkiness and can obstruct a surgeon's view. Electromagnetic actuators can also pose a safety risk due to the heat they emit as a result of the current they receive. 

\subsection{Proposed Solution}
We propose a design that places the actuation system under the operating table while only taking up limited space. We introduce optimization methods to solve the electromagnet (EM) arrangement problem leading to an E-optimal design (\textbf{TODO:} add appendix reference). 

\subsection{Inputs and Outputs}
\subsubsection{Inputs}
The program will receive the volume of the under-the-table workspace and properties of the EMs (\# of turns, area, current). In addition, the user will input their desired number of EMs in the system and the sample size (a larger size leads to a more optimal solution).

\subsubsection{Outputs}
The program will output the optimal positions of the EM actuators. 

\subsection{Stakeholders}
\subsubsection{General Stakeholders}
Surgeons and medical professionals that might operate an actuation system, engineers involved in the physical development of such systems, and researchers working on biomedical engineering systems and/or applications of optimization algorithms.

\subsubsection{Specialized Stakeholders}
Some specific stakeholders include Dr. Onaizah (HeART Lab), and Dr. Giamou (ARCO Lab).  

\subsection{Environment}
\subsubsection{Software}
A working Python environment is required. The software is compatible with Windows, MacOS, and Linux.

\subsubsection{Hardware}
More computing power will allow for more accurate results, but any personal computer should work. 

\section{Goals}

\section{Stretch Goals}

\section{Challenge Level and Extras}

\wss{State your expected challenge level (advanced, general or basic).  The
challenge can come through the required domain knowledge, the implementation or
something else.  Usually the greater the novelty of a project the greater its
challenge level.  You should include your rationale for the selected level.
Approval of the level will be part of the discussion with the instructor for
approving the project.  The challenge level, with the approval (or request) of
the instructor, can be modified over the course of the term.}

\wss{Teams may wish to include extras as either potential bonus grades, or to
make up for a less advanced challenge level.  Potential extras include usability
testing, code walkthroughs, user documentation, formal proof, GenderMag
personas, Design Thinking, etc.  Normally the maximum number of extras will be
two.  Approval of the extras will be part of the discussion with the instructor
for approving the project.  The extras, with the approval (or request) of the
instructor, can be modified over the course of the term.}

\newpage{}

\section*{Appendix --- Reflection}

\wss{Not required for CAS 741}

\input{../Reflection.tex}

\begin{enumerate}
    \item What went well while writing this deliverable? 
    \item What pain points did you experience during this deliverable, and how
    did you resolve them?
    \item How did you and your team adjust the scope of your goals to ensure
    they are suitable for a Capstone project (not overly ambitious but also of
    appropriate complexity for a senior design project)?
\end{enumerate}  

\end{document}